Music Versus No Music Effectiveness On Cognitive Response Time and Typing Efficiency

### 2024-03-29 paper/paper.tex
indent in vscode to fold

\documentclass[manuscript, screen, review]{acmart} %removing review removes the numbers on left side
% \documentclass was [sigconf]{acmart} changed to match with the given overleaf link
% \documentclass[sigconf]{acmart}

@@

% Put the related works here
% \section{Related Works}

>>>>

% \documentclass[manuscript, screen, review]{acmart} %removing review removes the numbers on left side
% \documentclass was [sigconf]{acmart} changed to match with the given overleaf link
\documentclass[sigconf]{acmart}

@@

% Put the related works here
\section{Related Works}
While there is not necessarily a concrete answer for whether music or background noise is effective on cognitive function, there have been many
studies that attempt to determine the answer.
